---
title: "p8105_hw6_jy3269"
author: "Jingyi Yao"
date: "`r Sys.Date()`"
output: github_document
---

```{r,include=F}
library(tidyverse)
library(modelr)
```


## Problem 2

### 1. Create `city_state` variable and a binary `solved` variable 
```{r}
raw_data <- read_csv("./data/homicide-data.csv",show_col_types = FALSE)
homicide <- raw_data %>% 
  mutate(
    city_state = str_c(city,", ",state),
    solved = ifelse(disposition == "Closed by arrest",1,0)) %>% 
  mutate(
      victim_sex = fct_relevel(victim_sex, "Female"),
      victim_race = fct_relevel(victim_race, "White"),
         ) 

homicide

```

## 2. Omit cities : Dallas, TX; Phoenix, AZ; and Kansas City, MO  and  Tulsa, AL
```{r}
homicide <- homicide %>% 
  filter(city_state != "Dallas, TX", city_state != "Phoenix, AZ", city_state != "Kansas City, MO", city_state != "Tulsa, AL")

```


## 3. Limit your analysis those for whom victim_race is white or black
```{r}
homicide <- homicide %>% 
  filter(victim_race == "White" | victim_race == "Black") %>% 
  mutate(victim_age = as.numeric(victim_age))

```

## 4. Select the predictors and response variable in Baltimore
```{r}
baltimore_df = 
  homicide %>% 
  filter(city == "Baltimore") %>% 
  select(solved, victim_age, victim_race, victim_sex)

baltimore_df

```


## 5. Fit logistic regression for Baltimore
```{r}
Baltimore_logistic = 
  baltimore_df %>% 
  glm(solved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())

```



## 6. Save the Baltimore model result as an R Object
```{r}
save(Baltimore_logistic, file = "./result/Baltimore_logistic.RData")

```



## 7. Tidy the object
```{r}
Baltimore_logistic %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)


```


## 8. Get the 95% CI of OR 
```{r}
alpha = 0.05

Baltimore_logistic %>% 
  broom::tidy() %>%
  mutate(OR = exp(estimate),
         OR_lower_bound = exp(confint(Baltimore_logistic)[,1]),
         OR_upper_bound = exp(confint(Baltimore_logistic)[,2]) )%>%
  filter(term == 'victim_sexMale') %>% 
  select(estimate, OR,OR_lower_bound,OR_upper_bound) %>% 
  knitr::kable(digits = 3)


```


The OR result shows that male victims in the homicides have a lower chance to have the case solved compared with women.


## 9.  Run `glm` for each of the cities
```{r,message=FALSE, warning=FALSE}
cities_logistic = 
  homicide %>% 
  select(city_state, victim_race:victim_sex, solved) %>% 
  nest(sample = victim_race:solved) %>% 
  mutate(
    models = map(sample, ~glm(solved ~ victim_age+victim_race+victim_sex, family= binomial(), data=.x)),
    results = map(models, broom::tidy),
    conf_int = map(models, ~confint(.x,"victim_sexMale"))
  ) %>% 
  select(city_state,results,conf_int) %>% 
  unnest(results) %>% 
  unnest_wider(conf_int) %>% 
  filter(term == "victim_sexMale") %>% 
  select(city_state,estimate,`2.5 %`,`97.5 %`) %>% 
  mutate(
    OR = exp(estimate),
    OR_lower_bound = exp(`2.5 %`),
    OR_upper_bound = exp(`97.5 %`)
    ) %>% 
  select(city_state,estimate,OR,OR_lower_bound,OR_upper_bound) 
```


```{r}
cities_logistic %>% knitr::kable(digits = 3)

```


```{r}
ggplot(cities_logistic, aes(y = fct_reorder(city_state, OR), x = OR)) +
  geom_point() +
  geom_errorbar(aes(xmin = OR_lower_bound, xmax = OR_upper_bound)) +
  labs(title = "Estimated OR and 95% CI", ) + ylab("City,State") + theme(axis.text.y = element_text(hjust = 0.5,size = 6))

```

\ \par
Comments on the plot :

  * Most of the estimated OR is less than 1. Thus, in most cities, the homicide whose victim is a male is less likely to be solved compared to those with a female victim.
  * Albuquerque, Stockton, Fresno, Nashville and Richmond have an estimated OR that is above 1. However, their 95% CI contains 1. Thus, we cannot conclude that there is significant difference between the odds of solving homicides for male and female victims in these cities.
  * Some cities' 95% CI does not contain 1, which means that there are significant difference between the odds of solving homicides for male and female victims in these cities. For example, New York, Chicago are cities with CI that does not contain 1.


\ \par
\ \par
## Problem 3

```{r,message=FALSE}
data <- read_csv("./data/birthweight.csv")
```

### 1. Clean the data for regression analysis

```{r}
birthwt <- data %>% 
  mutate(
    frace = recode(frace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown"),
    mrace = recode(mrace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other"),
    babysex = recode(babysex, `1` = "Male", `2` = "Female")
    ) %>% 
    filter(frace != "Unknown") %>% 
  mutate(
    frace = fct_relevel(frace, "White"),
    mrace = fct_relevel(mrace, "White"),
    babysex = fct_relevel(babysex,"Female")
         ) %>% 
  select(bwt,everything())

head(birthwt)


```


\ \par
Next, I will fit my linear model using the cleaned data. I examined the meaning of each variable and find it reasonable that all the variables may be relevant to the birth weight of a baby. Thus, I plan to fit the model using all the variables other than `bwt` (the response variable) as predictors to build a full model first. Then I will use the step-wise method to select significant variables backwards. The selected variables and the response variable build up my regression model.



## 2. Fit a full model 
```{r}
full_model <- lm(bwt ~., data = birthwt)

broom::tidy(full_model) %>%  knitr::kable()
  
```



## 3. Select variables in the full model 
```{r}
stepwise_model <- MASS::stepAIC(full_model, direction = "backward", trace = FALSE)
broom::tidy(stepwise_model) %>%  knitr::kable()


```


\ \par
As is shown in the stepwise_model result, the selected predictors are : babysex, bhead, blength, delwt, fincome, gaweeks, mheight, mrace, parity, ppwt, smoken. 


\ \par
The residual against fitted value plot is shown below.


## 4. Plot residuals vs. fitted values
```{r}
birthwt %>%  
  add_predictions(stepwise_model) %>% 
  add_residuals(stepwise_model) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point() +
  labs(title = "Residuals vs Fitted Values ", ) + xlab("Fitted Value") + ylab("Residuals")

```


## 5. Split dataset 
```{r}
cv_df = 
  crossv_mc(birthwt, 100) %>% 
  mutate(
    train = map(train, as_tibble), 
    test = map(test, as_tibble))

```



## 6. Compare the 3 models -- mean rmse
```{r,warning=FALSE}
cv_df %>% 
  mutate(
    my_model  = map(train, ~lm( bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
    model_2  = map(train, ~lm(bwt ~ gaweeks + blength, data = .x)),
    model_3  = map(train, ~lm(bwt ~ bhead*blength*babysex, data = .x))) %>% 
  mutate(
    rmse_my_model = map2_dbl(my_model, test, ~rmse(model = .x, data = .y)),
    rmse_2    = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y))) %>% 
  summarize(
    avg_rmse_my_model = mean(rmse_my_model),
    avg_rmse_model_2 = mean(rmse_2),
    avg_rmse_model_3  = mean(rmse_3)
  ) %>% 
  knitr::kable()



```



```{r,warning=FALSE}
cv_df %>% 
  mutate(
    my_model  = map(train, ~lm( bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
    model_2  = map(train, ~lm(bwt ~ gaweeks + blength, data = .x)),
    model_3  = map(train, ~lm(bwt ~ bhead*blength*babysex, data = .x))) %>% 
  mutate(
    rmse_my_model = map2_dbl(my_model, test, ~rmse(model = .x, data = .y)),
    rmse_2    = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y))) %>%
  select(starts_with("rmse")) %>%  
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin(aes(fill = model))
  

```

\ \par
According to the table and violin plot above, we know that my model has the lowest mean RMSE. The main effect model (model 2) has the highest RMSE. The interaction model (model 3) has RMSE slightly higher than my model.








