---
title: "p8105_hw6_jy3269"
author: "Jingyi Yao"
date: "`r Sys.Date()`"
output: html_document
---

```{r,include=F}
library(tidyverse)
library(modelr)
```


## Problem 2

### 1. Create `city_state` variable and a binary `solved` variable 
```{r}
raw_data <- read_csv("./data/homicide-data.csv",show_col_types = FALSE)
homicide <- raw_data %>% 
  mutate(
    city_state = str_c(city,", ",state),
    solved = ifelse(disposition == "Closed by arrest",1,0)) %>% 
  mutate(
      victim_sex = fct_relevel(victim_sex, "Female"),
      victim_race = fct_relevel(victim_race, "White"),
         ) 

homicide

```

## 2. Omit cities : Dallas, TX; Phoenix, AZ; and Kansas City, MO  and  Tulsa, AL
```{r}
homicide <- homicide %>% 
  filter(city_state != "Dallas, TX", city_state != "Phoenix, AZ", city_state != "Kansas City, MO", city_state != "Tulsa, AL")

```


## 3. Limit your analysis those for whom victim_race is white or black
```{r}
homicide <- homicide %>% 
  filter(victim_race == "White" | victim_race == "Black") %>% 
  mutate(victim_age = as.numeric(victim_age))

```

## 4. Select the predictors and response variable in Baltimore
```{r}
baltimore_df = 
  homicide %>% 
  filter(city == "Baltimore") %>% 
  select(solved, victim_age, victim_race, victim_sex)

baltimore_df

```


## 5. Fit logistic regression for Baltimore
```{r}
Baltimore_logistic = 
  baltimore_df %>% 
  glm(solved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())

confint(Baltimore_logistic)

```



## 6. Save the Baltimore model result as an R Object
```{r}
save(Baltimore_logistic, file = "./result/Baltimore_logistic.RData")

```



## 7. Tidy the object
```{r}
Baltimore_logistic %>% 
  broom::tidy() %>% 
  knitr::kable()


```


## 8. Get the 95% CI of OR and comparing male victims to female victims
```{r}
Baltimore_logistic %>% 
  broom::tidy() %>%
  mutate(OR = exp(estimate),
         lower_conf = exp(confint(Baltimore_logistic)[,1]),
         upper_conf = exp(confint(Baltimore_logistic)[,2])) %>%
  filter(term == 'victim_sexMale') %>% 
  select(estimate, OR,lower_conf,upper_conf) %>% 
  knitr::kable()


```


Therefore, in comparison to the baseline which is female, male has 0.425 times higher odds chance of getting a resolved case. Meaning that male has a lower chance to have a solved case than female.



```{r,message=FALSE, warning=FALSE}
cities_logistic = 
  homicide %>% 
  select(city_state, victim_race:victim_sex, solved) %>% 
  nest(sample = victim_race:solved) %>% 
  mutate(
    models = map(sample, ~glm(solved ~ victim_age+victim_race+victim_sex, family= binomial(), data=.x)),
    results = map(models, broom::tidy),
    conf_int = map(models, ~confint(.x,"victim_sexMale"))
  ) %>% 
  select(city_state,results,conf_int) %>% 
  unnest(results) %>% 
  unnest_wider(conf_int) %>% 
  filter(term == "victim_sexMale") %>% 
  select(city_state,estimate,`2.5 %`,`97.5 %`) %>% 
  mutate(
    OR = exp(estimate),
    `2.5 %` = exp(`2.5 %`),
    `97.5 %` = exp(`97.5 %`)
    ) %>% 
  select(city_state,estimate,OR,`2.5 %`,`97.5 %`) 
```


```{r}
cities_logistic %>% knitr::kable(digits = 3)

```


```{r}
ggplot(cities_logistic, aes(y = fct_reorder(city_state, OR), x = OR)) +
  geom_point() +
  geom_errorbar(aes(xmin = `2.5 %`, xmax = `97.5 %`)) +
  labs(title = "Adjusted OR and 95% CI", ) + ylab("City,State")+theme(axis.text.y = element_text(hjust = 0.5,size = 6))

```



## Problem 3

```{r,message=FALSE}
data <- read_csv("./data/birthweight.csv")

data
```

### 1. Clean the data for regression analysis

```{r}
birthwt <- data %>% 
  mutate(
    frace = recode(frace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown"),
    mrace = recode(mrace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other"),
    babysex = recode(babysex, `1` = "Male", `2` = "Female")
    ) %>% 
    filter(frace != "Unknown") %>% 
  mutate(
    frace = fct_relevel(frace, "White"),
    mrace = fct_relevel(mrace, "White"),
    babysex = fct_relevel(babysex,"Female")
         ) %>% 
  select(bwt,everything())

birthwt


```


```{r}



```


```{r}



```


```{r}



```


```{r}



```


```{r}



```


```{r}



```


```{r}



```










